---
title: "Human Activity Recognition Using Smartphones Dataset"
author: "Lalitha Pisapati"
date: "21 Sep 2015"
output: html_document
---

# Synopsis
This is an exersice to generate tidy data from raw data. The expectation is:
1. Merges the training and the test sets to create one data set.

2. Extracts only the measurements on the mean and standard deviation for each measurement.

3. Uses descriptive activity names to name the activities in the data set

4. Appropriately labels the data set with descriptive variable names.

5. From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

## Variable description
Column-1. Subject -  List of 30 volunteers within an age bracket of 19-48 years

Column-2. Activity - Each person performed six activities (WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING) wearing a smartphone (Samsung Galaxy S II) on the waist

Column-3:68. - Stats recorded using Accelerometer and Gyroscope. This was captured 3-axial linear acceleration and 3-axial angular velocity at a constant rate of 50Hz.
- Triaxial acceleration from the accelerometer (total acceleration) and the estimated body acceleration.
- Triaxial Angular velocity from the gyroscope. 
- A 561-feature vector with time and frequency domain variables. 

## Tidy Data Summary
```{r}
summary(dataSet2)
```

## Tidy Data column details
```{r}
str(dataSet2)
```

## Tidy Data sample data
```{r}
head(dataSet2)
```

*Generated on `r as.character(Sys.time())`*

